---
title: "Assignment2_445"
author: "Michael Rivera"
date: "2023-10-10"
output: pdf_document
---

## Question 1
Write a function that calculates the density function of a Uniform continuous variable on the interval  
(a,b)
 . The function is defined as
 
 We want to write a function `duniform(x, a, b)` that takes an arbitrary 
    value of `x` and parameters a and b and return the appropriate height of 
    the density function. For various values of `x`, `a`, and `b`, demonstrate 
    that your function returns the correct density value.
    
## a)  
Write your function without regard for it working with vectors of data. 
        Demonstrate that it works by calling the function with a three times, 
        once where $x< a$, once where $a < x < b$, and finally once where $b < x$.
```{r}
duniform <- function(x, a, b){
    if((x >= a) & (x<= b)){
      density <- (1/(b-a)) 
    }else{
      density <- 0}
  return(density)
}

a <- 1
b <- 2
x1 <- -1
x2 <- 1.5
x3 <- 3

duniform(x1, a, b)
duniform(x2, a, b)
duniform(x3, a, b)
```

## b)
Next we force our function to work correctly for a vector of `x` values. 
Modify your function in part (a) so that the core logic is inside a `for` 
statement and the loop moves through each element of `x` in succession. 
Your function should look something like this:
        
```{r}
duniform <- function(x, a, b){
  output <- NULL
  for( i in 1:length(x) ){  # Set the for loop to look at each element of x
    if(( x[i] >= a) & (x[i] <= b)){  
      # What should this logical expression be?
      output[i] <- (1/(b-a))
      # ???  Something ought to be saved in output[i]
    }else{
      output[i] <- 0
      # ???  Something else ought to be saved in output[i]
    }
  }
  return(output)
}
```

Verify that your function works correctly by running the following code:
```{r}
data.frame( x=seq(-1, 12, by=.001) ) %>%
  mutate( y = duniform(x, 4, 8) ) %>%
  ggplot( aes(x=x, y=y) ) +
  geom_step()
```
## C) Install the R package microbenchmark. We will use this to discover the average duration your function takes.
```{r}
# install.packages("microbenchmark")
microbenchmark::microbenchmark( duniform( seq(-4,12,by=.0001), 4, 8), times=100)
```
## d) Instead of using a for loop, it might have been easier to use an ifelse() command. Rewrite your function to avoid the for loop and just use an ifelse() command. Verify that your function works correctly by producing a plot, and also run the microbenchmark(). Which version of your function was easier to write? Which ran faster?

```{r}
duniformifelse <- function(x, a, b){
  output <- NULL
  output <- ifelse( (x >= a) & (x <= b), (1/(b-a)), 0)
  return(output)
}
```

```{r}
data.frame( x=seq(-1, 12, by=.001) ) %>%
  mutate( y = duniformifelse(x, 4, 8) ) %>%
  ggplot( aes(x=x, y=y) ) +
  geom_step()
```

```{r}
# install.packages("microbenchmark")
microbenchmark::microbenchmark( duniformifelse( seq(-4,12,by=.0001), 4, 8), times=100)
```
The ifelse version ran much faster (mean was about 8 compared to 60 ms) and the ifelse was much easier for me to write, although I went back and look at chapter 6 between classes first.

## question 2
I very often want to provide default values to a parameter that I pass to a function. For example, it is so common for me to use the pnorm() and qnorm() functions on the standard normal, that R will automatically use mean=0 and sd=1 parameters unless you tell R otherwise. To get that behavior, we just set the default parameter values in the definition.

When the function is called, the user specified value is used, but if none is specified, the defaults are used. Look at the help page for the functions dunif(), and notice that there are a number of default parameters

For your duniform() function provide default values of 0 and 1 for a and b. Demonstrate that your function is appropriately using the given default values.

```{r}
duniformifelse <- function(x, a=0, b=1){
  output <- NULL
  output <- ifelse( (x >= a) & (x <= b), (1/(b-a)), 0)
  return(output)
}
```

```{r}
duniformifelse(x1, a, b)
duniformifelse(x2, a, b)
duniformifelse(x3, a, b)
```


```{r}
data.frame( x=seq(-1, 12, by=.001) ) %>%
  mutate( y = duniformifelse(x) ) %>%
  ggplot( aes(x=x, y=y) ) +
  geom_step()
```

## Question 3
A common data processing step is to standardize numeric variables by subtracting the mean and dividing by the standard deviation. Mathematically, the standardized value is defined as

where 

¯
x is the mean and   s  is the standard deviation. 
  

Create a function that takes an input vector of numerical values and produces an output vector of the standardized values. 

We will then apply this function to each numeric column in a data frame using the dplyr::across() or the dplyr::mutate_if() commands. 

This is often done in model algorithms that rely on numerical optimization methods to find a solution. 

By keeping the scales of different predictor covariates the same, the numerical optimization routines generally work better.

```{r}
standardize <- function(x){
  output <- NULL
  xbar <- mean(x)
  s <- sd(x)
  output <- ((x - xbar)/(s))
  return(output)
  
  ## What goes here?
}

data( 'iris' )
# Graph the pre-transformed data.
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
  geom_point() +
  labs(title='Pre-Transformation')

# Standardize all of the numeric columns
# across() selects columns and applies a function to them
# there column select requires a dplyr column select command such
# as starts_with(), contains(), or where().  The where() command
# allows us to use some logical function on the column to decide
# if the function should be applied or not.
iris.z <- iris %>% mutate( across(where(is.numeric), standardize) )

# Graph the post-transformed data.
ggplot(iris.z, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
  geom_point() +
  labs(title='Post-Transformation')
```

## Question 4
In this example, we’ll write a function that will output a vector of the first  n  terms in the child’s game Fizz Buzz.

The goal is to count as high as you can, but for any number evenly divisible by 3, substitute “Fizz” and any number evenly divisible by 5, substitute “Buzz,” and if it is divisible by both, substitute “Fizz Buzz.”

So the sequence will look like 1, 2, Fizz, 4, Buzz, Fizz, 7, 8, Fizz, ...
Hint: The paste() function will squish strings together, the remainder operator is %% where it is used as 9 %% 3 = 0.

```{r}
fizzbuzz <- function(runtime){
output <- ''
for(i in 1:runtime){
  if((i %% 3==0) & (i %% 5==0)){
    output <- paste(output, 'FizzBuzz')
  }
  else if (i %% 3==0){
    output <- paste(output, 'Fizz')
  }
  else if (i %% 5==0){
    output <- paste(output, 'Buzz')
  }
  else{
    output <- paste(output, i)
  }
  
}
return(output)
}
fizzbuzz(20)

#HARD
```
## Question 5
The  dplyr::fill()  function takes a table column that has missing values and fills them with the most recent non-missing value. For this problem, we will create our own function to do the same.

```{r}
#' Fill in missing values in a vector with the previous value.
#' 
#' @parm x An input vector with missing values
#' @result The input vector with NA values filled in.
myFill <- function(x){
  # Stuff in here!
}
```

```{r}
myFill <- function(x){
  store <- NULL
  for(i in 1:length(x)){
    if (is.na(x[i])){
    store[i] <- store[i-1]
  }
    else{
    store[i] <- x[i]
  }
  
  }
  return(store)
}
```

```{r}
test.vector <- c('A',NA,NA, 'B','C', NA,NA,NA)
myFill(test.vector)
```

















```{r}
# Simplest version
if( logical.test ){ # The logical test must be a SINGLE TRUE/FALSE value
  expression        # The expression could be many lines of code
}

# Including the optional else
if( logical.test ){
  expression
}else{
  expression
}
```















