---
title: "Assignment2_445"
author: "Michael Rivera"
date: "2023-10-17"
output: pdf_document
---

## Question 1

```{r}

```

## Question 2
```{r}

```




## Question 3

```{r}

```


## Question 1
For the following regular expression, explain in words what it matches on. Then add test strings to demonstrate that it in fact does match on the pattern you claim it does. 

Make sure that your test set of strings has several examples that match as well as several that do not.

If you copy the Rmarkdown code for these exercises directly from my source pages, make sure to remove the eval=FALSE from the R-chunk headers.

a. This regular expression matches: Insert your answer here…

strings that contain the character 'a', but, crucially, not 'A', which is why 'Anne' returns a FALSE, while 'Michael' returns a TRUE
```{r}
strings <- c('Anne', 'Michael', 'Evan', 'Zeke')
        data.frame( string = strings ) %>%
          mutate( result = str_detect(string, 'a') )
```

b. This regular expression matches: Insert your answer here…
This expression detects if your string contains 'ab' anywhere in the string, but, crucially, this still does not include capitalization, such as with 'Abby'.

```{r}

strings <- c('Abby', 'Gabby', 'jab', 'ACAB')
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, 'ab') )
```

c)  This regular expression matches:  *Insert your answer here...*
This expression searches for if the strings contain either 'a' or 'b' as a character, even if only one is present. This still does not include capitalization 'AB'.
        
```{r}
        strings <- c('AB', 'ab', 'Jab', 'Abby', 'Gabby')
        data.frame( string = strings ) %>%
          mutate( result = str_detect(string, '[ab]') )
```
d)  This regular expression matches:  *Insert your answer here...*
This expression is looking for the characters 'ab' in a string, but only at the beginning of a string as indicated by the ^.
```{r}
        strings <- c('ab', 'Gabby', 'Abby', 'JaB', 'abbyyy')
        data.frame( string = strings ) %>%
          mutate( result = str_detect(string, '^[ab]') )
```
e. This expression detects within the strings if there are any digits that are separated by white space from the characters 'a' or 'A'
```{r}
strings <- c('13 aA', 'a 123', '123 a', 'r123A', 'r123 A')
        data.frame( string = strings ) %>%
          mutate( result = str_detect(string, '\\d+\\s[aA]') )
```
f. This expression detects if there are any digits which are followed by zero or more white space containing the characters 'a' or 'A'
```{r}
        strings <- c('13 aA', 'a 123', '123 a', 'r123A', 'r123 A', 'a123 a', 'a123')
        data.frame( string = strings ) %>%
          mutate( result = str_detect(string, '\\d+\\s*[aA]') )
```
g.This expression detects if any character  of any length exists. this includes ' '. 
```{r}
        strings <- c('', 'a', '123', 'eeee', 'WEWEWE')
        data.frame( string = strings ) %>%
          mutate( result = str_detect(string, '.*') )
```
h. this expression detects if the beginning of a given string contains two alphanumeric characters prior to the characters 'bar'. 
```{r}
        strings <- c('1', '11bar', '11 bar', 'd11bar', '11bard')
        data.frame( string = strings ) %>%
          mutate( result = str_detect(string, '^\\w{2}bar') )
```
i.this expression detects if a given string contains 'foo' followed by a '.' character, followed by 'bar'
```{r}
        strings <- c('foo.bar', 'foobar', '11bar')
        data.frame( string = strings ) %>%
          mutate( result = str_detect(string, '(foo\\.bar)|(^\\w{2}bar)') )
```


## Question 2
The following file names were used in a camera trap study. 

S number represents the site, 
P is the plot within a site, 
C is the camera number within the plot, 

the first string of numbers is the

YearMonthDay 

and the second string of numbers is the 

HourMinuteSecond.

```{r}
file.names <- c( 'S123.P2.C10_20120621_213422.jpg',
                 'S10.P1.C1_20120622_050148.jpg',
                 'S187.P2.C2_20120702_023501.jpg')
```

Produce a data frame with columns corresponding to the site, plot, camera, year, month, day, hour, minute, and second for these three file names. So we want to produce code that will create the data frame:
```{r}
camframe <- c('site', 'plot', 'camera', 'year', 'month', 'day', 'hour', 'minute', 'second')

filenames2 <- str_replace_all(file.names, pattern = '_', replacement = '\\.')

filenames2
```


```{r}
filenames3 <- str_split_fixed(filenames2, pattern = '\\.', 6)


Year <- str_sub(filenames3[,4], start = 1, end = 4) 
month <- str_sub(filenames3[,4], start = 5, end = 6)
day <- str_sub(filenames3[,4], start = 7, end = 8)

hour <- str_sub(filenames3[,5], start = 1, end = 2)
minute <- str_sub(filenames3[,5], start = 3, end = 4)
second <- str_sub(filenames3[,5], start = 5, end = 6)


ffile <- cbind(filenames3, Year, month, day, hour, minute, second)
ffile

ffileDF <- data.frame(ffile)

colnames(ffileDF) <- c('site', 'plot', 'camera', 'ymd', 'hms', 'filetype', 'year', 'month', 'day', 'hour', 'minute', 'second')

ffileDF %>%
   select('site', 'plot', 'camera', 'year', 'month', 'day', 'hour', 'minute', 'second')
```



## Question 3
The full text from Lincoln’s Gettysburg Address is given below. 

Calculate the mean word length Note: consider ‘battle-field’ as one word with 11 letters).

```{r}
Gettysburg <- 'Four score and seven years ago our fathers brought forth on this continent, a new nation, conceived in Liberty, and dedicated to the proposition that all men are created equal. Now we are engaged in a great civil war, testing whether that nation, or any nation so conceived and so dedicated, can long endure. We are met on a great battle-field of that war. We have come to dedicate a portion of that field, as a final resting place for those who here gave their lives that that nation might live. It is altogether fitting and proper that we should do this. But, in a larger sense, we can not dedicate -- we can not consecrate -- we can not hallow -- this ground. The brave men, living and dead, who struggled here, have consecrated it, far above our poor power to add or detract. The world will little note, nor long remember what we say here, but it can never forget what they did here. It is for us the living, rather, to be dedicated here to the unfinished work which they who fought here have thus far so nobly advanced. It is rather for us to be here dedicated to the great task remaining before us -- that from these honored dead we take increased devotion to that cause for which they gave the last full measure of devotion -- that we here highly resolve that these dead shall not have died in vain -- that this nation, under God, shall have a new birth of freedom -- and that government of the people, by the people, for the people, shall not perish from the earth.'
```

```{r}
Gettysburg2 <- str_replace_all(Gettysburg, pattern = ',', replacement = '')

Gettysburg2 <- str_replace_all(Gettysburg2, pattern = '-', replacement = '')

Gettysburg2 <- str_replace_all(Gettysburg2, pattern = '\\.', replacement = '')

get_split <- scan(text = Gettysburg2, what = ' ')

totalchar <- 0
words <- 0
for (i in 1:length(get_split)){
  word_len <- str_length(get_split[i])
  totalchar <- totalchar + word_len
  words <- words + 1
}

meanchar <- totalchar/words
meanchar

totalchar
get_split
Gettysburg2
```
