---
title: "GSP445Assignment4"
author: "Michael Rivera"
date: "2023-10-26"
output: pdf_document
---

```{r}
library(tidyr)
library(dplyr)
library(tidyverse)
```

## Question 1
A common task is to take a set of data that has multiple categorical variables and create a table of the number of cases for each combination. 

An introductory statistics textbook contains a dataset summarizing student surveys from several sections of an intro class. 

The two variables of interest for us are Gender and Year which are the students gender and year in college.

a. Download the dataset and correctly order the Year variable using the following:
```{r}
Survey <- read.csv('https://www.lock5stat.com/datasets3e/StudentSurvey.csv', na.strings=c('',' ')) 
```

b. Using some combination of dplyr functions, produce a data set with eight rows that contains the number of responses for each gender:year combination. 

Make sure your table orders the Year variable in the correct order of First Year, Sophmore, Junior, and then Senior. 

You might want to look at the following functions: dplyr::count and dplyr::drop_na.


```{r}
survey.2 <- Survey %>%
  select(., Year, Sex) %>%
  count(Year, Sex) 


#Survey %>% group_by(Year, Sex) %>% summarize(Count = n())

Survey2 <- Survey %>% 
  count(Year, Sex)

Survey2

Survey2 <- drop_na(Survey2)

Survey2 %>%
  pivot_wider(
    names_from = Year, 
    values_from = n
  )
```

```{r}

```

```{r}

```
































