---
title: "STA445Assignment5mar924"
author: "Michael Rivera"
date: "2023-11-09"
output: pdf_document
---

```{r setup}
library(tidyverse)   # loading ggplot2 and dplyr
library(patchwork)   # arranging multiple graphs into 1 figure
library(viridis)     # The viridis color schemes
library(latex2exp)   # For plotting math notation
library(plotly)     # for interactive hover-text
```

## Question 1
The infmort data set from the package faraway gives the infant mortality rate for a variety of countries. The information is relatively out of date (from 1970s?), but will be fun to graph. 

Visualize the data using by creating scatter plots of mortality vs income while faceting using region and setting color by oil export status. Utilize a  
log
10
  
transformation for both mortality and income axes.

This can be done either by doing the transformation inside the aes() command or by utilizing the scale_x_log10() or scale_y_log10() layers. 

The critical difference is if the scales are on the original vs log transformed scale. Experiment with both and see which you prefer.

```{r}
library(faraway)
data(infmort)
```

a. The rownames() of the table gives the country names and you should create a new column that contains the country names. *rownames
```{r}
rownames(infmort)
Ninfmort <- infmort
NNinfmort <- Ninfmort %>%
  mutate(
    countryname = (rownames(infmort))
  )

NNinfmort
```

b. Create scatter plots with the log10() transformation inside the aes() command.
```{r}
ggplot(NNinfmort, aes(x=log10(income), y=mortality)) +
  geom_point() +
  
  facet_wrap(. ~region)
```

c. Create the scatter plots using the scale_x_log10() and scale_y_log10(). Set the major and minor breaks to be useful and aesthetically pleasing. Comment on which version you find easier to read.
```{r}
#ggplot(NNinfmort, aes(x=income, y=log10(mortality))) +
  #geom_point()

library(cowplot)

cowplot::plot_grid(
  ggplot(NNinfmort, aes(x=income, y=mortality )) +
    geom_point() +
    scale_x_log10(breaks=c(100, 1000, 5000),
                  minor=c(50, 500, 2500)) +
    scale_y_log10(breaks=c(200, 800, 400, 100)) +
    facet_wrap(. ~region)
)
```
d. The package ggrepel contains functions geom_text_repel() and geom_label_repel() that mimic the basic geom_text() and geom_label() functions in ggplot2, but work to make sure the labels don’t overlap. Select 10-15 countries to label and do so using the geom_text_repel() function.

```{r}
library(ggrepel)
plot <- NNinfmort
plot2 <- slice_sample(NNinfmort, n=10)
plot3 <- ggplot(plot2, aes(x=income, y=mortality, label = countryname)) +
    geom_point() +
    scale_x_log10(breaks=c(100, 1000, 5000),
                  minor=c(50, 500, 2500)) +
    scale_y_log10(breaks=c(200, 800, 400, 100)) 

plot4 <- plot3 + geom_text_repel() + labs(title = 'Title')

plot4

#mutate new column country
#str detect ifelse if country has 'r' else 'NA'
```



## Question 2
Using the datasets::trees data, complete the following:
a. Create a regression model for 
y = Volume as a function of 
x = Height.

```{r}
data(trees)
trees
x <- trees$Height
y <- trees$Volume

TreeModel <- lm(y~x)
TreeModel
```

b. Using the summary command, get the y-intercept and slope of the regression line.

```{r}
#summary(trees)
x <- trees$Height
y <- trees$Volume

TreeModel <- lm(y~x)
TreeModel

y_intercept <- TreeModel$coefficients[[1]]
slopeee <- TreeModel$coefficients[[2]]
summary(TreeModel)
```
c. Using ggplot2, create a scatter plot of Volume vs Height.

```{r}
ggplot(trees, aes(x=Volume, y=Height)) +
  geom_point()
```
d. Create a nice white filled rectangle to add text information to using by adding the following annotation layer.

```{r}
ggplot(trees, aes(x=Volume, y=Height)) +
  geom_point() +
  annotate('rect', xmin=65, xmax=75, ymin=60, ymax=74,
         fill='white', color='black') 
```
e. Add some annotation text to write the equation of the line
        $\hat{y}_i = -87.12 + 1.54 * x_i$ in the text area.

```{r}
ggplot(trees, aes(x=Height, y=Volume)) +
  geom_point() +
  annotate('rect', xmin=63, xmax=77, ymin=60, ymax=74, fill='white', color='black',
           ) +
  annotate('text', x=70, y=65, xmin=65, xmax=75, ymin=60, ymax=74,
           label = latex2exp::TeX('$\\hat{y}_i = -87.12 + 1.54 * x_i$'))
```
f. Add annotation to add $R^2 = 0.358$
```{r}
ggplot(trees, aes(x=Height, y=Volume)) +
  geom_point() +
  annotate('rect', xmin=63, xmax=77, ymin=60, ymax=74, fill='white', color='black',
           ) +
  annotate('text', x=70, y=65, xmin=65, xmax=75, ymin=60, ymax=74,
           label = latex2exp::TeX('$\\hat{y}_i = -87.12 + 1.54 * x_i$')) +
  annotate('text', x=70, y=47, xmin=65, xmax=75, ymin=60, ymax=74,
           label = latex2exp::TeX('$R^2 = 0.358$'))
```
g. Add the regression line in red. The most convenient layer function to uses
        is `geom_abline()`. It appears that the `annotate` doesn't work with
        `geom_abline()` so you'll have to call it directly.
```{r}
ggplot(trees, aes(x=Height, y=Volume)) +
  geom_point() +
  geom_abline(slope = slopeee, intercept = y_intercept, color='red') +
  annotate('rect', xmin=63, xmax=77, ymin=60, ymax=74, fill='white', color='black',
           ) +
  annotate('text', x=70, y=65, xmin=65, xmax=75, ymin=60, ymax=74,
           label = latex2exp::TeX('$\\hat{y}_i = -87.12 + 1.54 * x_i$')) +
  annotate('text', x=70, y=47, xmin=65, xmax=75, ymin=60, ymax=74,
           label = latex2exp::TeX('$R^2 = 0.358$'))
```
























